
```{r setup, include=FALSE, echo = FALSE}

```
#About SpotR

##What is SpotR?
**SpotR** is an interactive web app that creates visual graphics out of your playlist data. We directly source track and playlist data from the [Spotify Web Api](https://developer.spotify.com/web-api/). With SpotR, users have the power to enter a specific Spotify User id, and bring up visuals regarding their playlist information. With this app, we give Spotify users **the power to visualize their music playlist consumption.**

Through the Spotify Web Api, we are able to source:
```{r list, echo=FALSE}
markdown.list = "
- Artists
- Playlists (User and Chart Top 50's)
- Tracks
- Genres
- Release Date
- Explicit/Non-Explicit
"
```
`r markdown.list`

##How it Works
We utilized the **HTTR**, **JSONLITE**, and **DPLYR** packages to access, retrieve, and wrangle the Spotify data. By compiling data frames with song and playlist info, we then utilized package **PLOTLY** to generate the data charts. Finally, with the **SHINY** package, we compiled everything up to make our data interactive with users.

##The Team
- **Kris Wong**  
<iframe src="https://open.spotify.com/follow/1/?uri=spotify:user:12158467793&size=detail&theme=light" width="300" height="56" scrolling="no" frameborder="0" style="border:none; overflow:hidden;" allowtransparency="true"></iframe>

- **Clem Mooc**  
<iframe src="https://open.spotify.com/follow/1/?uri=spotify:user:1262636354&size=detail&theme=light" width="300" height="56" scrolling="no" frameborder="0" style="border:none; overflow:hidden;" allowtransparency="true"></iframe>

- **Thomas Penner**  
<iframe src="https://open.spotify.com/follow/1/?uri=spotify:user:22stxix34kkqknmrl5wov2jgy&size=detail&theme=light" width="300" height="56" scrolling="no" frameborder="0" style="border:none; overflow:hidden;" allowtransparency="true"></iframe>

- **Gyubeom (Jason) Kim**  